---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Databoard-Package 

<!-- badges: start -->

<!-- badges: end -->

Automated Content Coding with Large Language Models

## Getting started

```{r, eval=FALSE}         
# Install the package (see below), then load it
library(databoard)

# Get access token from your individual username and password and store it invisibly in the system environment
get_token("username", "pw")

# Submit a task to the databoard servive
submit_task(input, 
submit_task()
```

See further examples in `vignette("gettingstarted", package="databoard")`.

## Concept

The databoard package is made for easily accessing the databoard service, which helps to automatically code, summarize or tokenize textual content. 

## Examples

### Data preparation  



## Authors and citation

**Authors**\

Jakob Jünger (University of Münster)\
Katharina Maubach (University of Münster)\

**Citation**\


