---
title: "Use custom prompts and additional parameters"
output: html_document
vignette: >
  %\VignetteIndexEntry{Custom Prompts}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}

library(dplyr)
library(tibble)

knitr::opts_chunk$set(eval=FALSE, include=TRUE)
```

## Prepare data and login

To prepare the following examples, load the package and example data. 
Then log into the service (see the introduction vignette for further information). 

```{r}

# Load package
library(databoard)

# Load example data
df <- databoard::movies
rules <- databoard::movies_rules

# Login
da_login()

```

## Custom prompts

The datavana service is based on [precomposed prompts](https://github.com/datavana/databoard_core/tree/main/src/databoard_core/resources/prompts) for the different workflows.
You can override the default prompt templates and by-pass all post-processing to get direct LLM answers using the `llm_prompt()` function. Provide your prompts in the `prompt.user`- and `prompt.system`-parameters.

In the prompts, for each case in the input data frame `df`,
the placeholder `{{text}}` will be replaced 
by the content of the selected `abstract` column.


```{r}

# Submit tasks
results <- llm_prompt(
  df, abstract,
  
  prompt.system = paste0(
    "Output a comma separated list of categories. ",
    "Just the list, nothing else. ",
    "The possible categories are: scifi, historical, drama, comedy, fantasy, romance"
  ),
  
  prompt.user = "{{text}}"
  
)


# Fetch results
results <- llm_prompt(custom)

```

*Note:* In the previous example, we used `paste0()` to concatenate the sentences. 
This serves readability, alternatively, you can provide the prompt as one single character string.

## Adapt prompts for the existing workflow methods

Instead of using the `llm_prompt()`-function, you can also adapt the prompts
used by the workflow-specific functions `llm_summarize()`,  `llm_code()` or `llm_annotate()`.
Using this technique, you can leverage the pre- and post-processing steps of the Databoard service.
For example, when providing rules, the result is automatically split it into one field for each category. By the way: under the hood, the `llm_prompt()` function uses the summary workflow with settings that simply disable result processing.

In your prompt templates, use the `{{text}}` placeholder to define the slot where the content of your data frame will be inserted. 

The `{{rules}}` placeholder will be replaced by a markdown formatted list of all the rules provided in the rules book. When using rules, make sure your prompt is compatible with the expected pattern. 
The post-processing procedure expects one line for each output column. 
whatever follows the category name will be inserted into the column.

To enter line breaks into a prompt, use the escape sequence `\n`.


```{r}

results <- llm_summarize(
  movies, abstract, rules, 
  
  options = list(
      prompts = list(
        system = paste0(
          "You are an expert in content analysis. Be precise and concise.",
          "Use the codebook provided to decide for each category, ",
          "whether the given text falls into the category. ",
          
          "Return one line for each category. ",
          "Each returned line must start with the category name ", 
          "followed by a colon ':' and then followed by one of the codes ",
          
          "'5' if the category applies fully, ",
          "'4' if the category mostly applies, ",
          "'3' if the category partially applies, ", 
          "'2' if the category mostly does not apply, ",
          "'1' if the category does not apply at all. ", 
          
          "Return only the lines for each category - ",
          "nothing else, no introduction, no explanation, no disclaimer!\n",
          
          "# Rules:\n {{rules}}\n"
        ),
        user = "{{text}}"
     )
   )
)

results <- llm_summarize(results)

```



## Additional parameters

We have implemented additional parameters to control the model choice (model, temperature), the job queue (wait-parameter) and the processing steps (mode-parameter).

### Wait parameter

The service is designed to be called multiple times to gather all results irrespective of wait time. 
You first submit the jobs and than poll until all results are finished.

The wait parameter describes the time in seconds the service waits for result from the LLM for each request (default = 0, values range from 0 to 10). For typical use cases, the default of zero is the most sensible choice. But if your data set is small and you know that answers will be available fast, you
can increase the wait time and if you are lucky, results will be available directly after submitting the tasks:


```{r}

results <- llm_summarize(df, review, wait = 10)

```

### Mode parameter

Some workflows can return multiple values per case, for example when coding text with multiple categories
or when summarizing text with multiple rules.

Only `llm_code()` exposes an explicit `mode` argument.
It controls how the coding result is structured:

- `single` (default): return the single best-matching category per case.
- `multi`: return one value per category, where `2` means the category strongly applies, `1` means it applies, and `0` means it does not apply.

```{r}
# Single mode (default)

results <- llm_code(df, abstract, rules, mode = "single")
results <- llm_code(results)

# Multi mode

results <- llm_code(df, abstract, rules, mode = "multi")
results <- llm_code(results)

```


The `llm_summarize()` method uses the same idea internally, but switches automatically: 
with `rules` it returns one result per rule, otherwise it returns a single summary per case. A typical use case for multi-mode is extracting information such as a movie's year, the topic or the main character's name. Example:

```{r}

rules <- tibble::tribble(
  ~category,  ~description,                                  ~example,
  "figure",   "The names of the main characters in the movie", "John Doe",
  "gender",   "The gender of the main characters",             "male"
)

results <- llm_summarize(df, abstract, rules)
results <- llm_summarize(results)
```


### Model parameters

The workflow wrappers forward model-related settings via the `options` list.
The most common ones are:

- **model**: choose the LLM model to use.
- **temperature**: control how deterministic or varied the answer should be.

See the databoard [API documentation](https://databoard.uni-muenster.de/docs#/default/task_add_tasks_run_post) for a complete list of available options and their values.
If you do not set these options, the server defaults are used.

For example:

```{r}

results <- llm_code(
  df, abstract, rules, 
  
  options = list(
    model = 'mistral-small',
    temperature = "2"
  )
)

results <- llm_code(results)

```
