---
title: "Create custom prompts and include additional parameters"
output: html_document
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}

library(dplyr)
library(tibble)

knitr::opts_chunk$set(eval=FALSE, include=TRUE)
```

## Prepare data and login

To prepare the following examples, load the package and example data. 
Then log into the service (see the introduction vignette for further information). 

```{r}

# Load package
library(databoard)

# Load example data
df <- databoard::movies
rules <- databoard::movies_rules

# Login
da_login()

```

## Custom prompts

You can use custom prompt templates and by-pass all post-processing to get direct LLM answers.
using the `llm_prompt()` function. Provide your prompts in the `prompt.user`- and `prompt.system`-parameters.

In the prompts, for each case in the input data frame `df`,
the placeholder `{{text}}` will be replaced 
by the content of the selected `abstract` column.


```{r}

# Submit tasks
results <- llm_prompt(
  df, abstract,
  
  prompt.system = paste0(
    "Output a comma separated list of categories. ",
    "Just the list, nothing else. ",
    "The possible categories are: scifi, historical, drama, comedy, fantasy, romance"
  ),
  
  prompt.user = "{{text}}"
  
)


# Fetch results
results <- llm_prompt(custom)

```

*Note:* In the previous example, we used `paste0()` to concatenate the sentences. 
This serves readability, alternatively, you can provide the prompt as one single character string.


## Adapt prompts for the existing workflow methods

Instead of using the `llm_prompt()`-function, you can also adapt the prompts
used by the workflow-specific functions such as `llm_summarize()` or `llm_code()`.
Using this technique, you can leverage the pre- and post-processing steps of the Databoard service. 
For example, when providing rules, the result is automatically split it into one field for each category.

Use the `{{text}}` placeholder to define the slot where the content of your data frame will be inserted. 

The `{{rules}}` placeholder will be replaced by a markdown formatted list of all the rules provided in the rules book. When using rules, make sure your prompt is compatible with the expected pattern. 
The post-processing procedure expects one line for each output column. 
whatever follows the category name will be inserted into the column.

To enter line breaks into a prompt, use the escape sequence `\n`.


```{r}

custom_results <- llm_summarize(
  movies, abstract, rules, 
  
  options = list(
      prompts = list(
        system = paste0(
          "You are an expert in content analysis. Be precise and concise.",
          "Use the codebook provided to decide for each category, ",
          "whether the given text falls into the category. ",
          
          "Return one line for each category. ",
          "Each returned line must start with the category name ", 
          "followed by a colon ':' and then followed by one of the codes ",
          
          "'5' if the category applies fully, ",
          "'4' if the category mostly applies, ",
          "'3' if the category partially applies, ", 
          "'2' if the category mostly does not apply, ",
          "'1' if the category does not apply at all. ", 
          
          "Return only the lines for each category - ",
          "nothing else, no introduction, no explanation, no disclaimer!\n",
          
          "# Rules:\n {{rules}}\n"
        ),
        user = "{{text}}"
     )
   )
)

custom_results <- llm_summarize(custom_results)

```



## Additional parameters

We have implemented additional parameters to control the model choice (model, temperature),
the job queue (wait-parameter) and the processing steps (mode-parameter).

### Wait parameter

The service is designed to be called multiple times to gather all results irrespective of wait time. 
You first submit the jobs and than poll until all results are finished.

The wait parameter describes the time in seconds the service waits for result from the LLM for each request (default = 0, values range from 0 to 10). For typical use cases, the default of zero is the most sensible choice. But if your data set is small and you know that answers will be available fast, you
can increase the wait time and if you are lucky, results will be available directly after submitting the tasks:


```{r}

results <- llm_summarize(df, review, wait = 10)

```

### Mode parameter

The coding  workflow has multiple modes to process the data. These modes describe different system prompts (see [here](https://github.com/datavana/databoard_core/tree/main/src/databoard_core/resources/prompts) for the exact prompts). We differentiate between:

- single mode (default): categorizes each text into the most appropriate category 
- multi mode: Determines for each category whether it strongly applies (2), applies (1) or does not apply.

```{r}
# Coding Single Mode (default)

results_single <- llm_code(df, abstract, rules)
results_single <- llm_code(results_single)
count(results_single, llm_result)

# Coding Multi Mode

results_multi <- llm_code(df, abstract, rules, mode = "multi")
results_multi <- llm_code(results_multi)

```

You can also build your own custom prompts using the llm_summarize function (see below).

### Model parameters

Additionally to the parameters the package supports a list of options that can be passed to the functions. These include the model choice, the temperature and the amount of preprocessing. 

- **model**: Choose a LLM model. Supported models include ```'Llama-3.3-70B' (default)```, ```'mistral-small'```, ```'gemma-3-27b-it'```, ```'gemma-3'```, ```'gpt-oss-120b'```, ```'Apertus-8B-Instruct-2509'```. 
- **temperature**: Overrides the server default which is (NOT_GIVEN)

All these options can be called in the functions as follows:

```{r}
results_options <- llm_code(
  df, abstract, rules, 
  options = list(
    model = 'mistral-small',
    temperature = "2"
  )
)

results_options <- llm_code(results_options)

```
