---
title: "Create custom prompts and include additional parameters"
output: html_document
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}

library(dplyr)
library(tibble)
knitr::opts_chunk$set(eval=F, include=T)
```

## Prepare data and login

In a first step we load the package and data and login into the service 
(see vignette introduction for further information). 

```{r}
library(databoard)
df <- databoard::movies # example data 
rules <- databoard::movies_rules
da_login()
```

## Additional Parameters for using the databoard

We have implemented additional parameters for the summary and coding process. 
These include the wait and the mode parameter as well as a list of additional options (model choice, temperature and pre-processing).

### Wait Parameter

The wait parameter describes the time (in seconds) the service waits for each request (default = 0, values range from 0 to 10). Note that the service is designed to be called multiple times to gather all results irrespective of wait time. Therefore for typical usecases the default of zero waittime is the most sensible. 

```{r}
# Wait Parameter
results <- llm_summarize(df, review, wait = 10)
```

### Mode Parameter

The coding  workflow has multiple modes to process the data. These modes describe different system prompts (see [here](https://github.com/datavana/databoard_core/tree/main/src/databoard_core/resources/prompts) for the exact prompts). We differentiate between:

- single mode (default): categorizes each text into the most appropriate category 
- multi mode: Determines for each category whether it strongly applies (2), applies (1) or does not apply.

```{r}
# Coding Single Mode (default)

results_single <- llm_code(df, abstract, rules)
results_single <- llm_code(results_single)
count(results_single, llm_result)

# Coding Multi Mode

results_multi <- llm_code(df, abstract, rules, mode = "multi")
results_multi <- llm_code(results_multi)
View(results_multi)
```

You can also build your own custom prompts using the llm_summarize function (see below).

### Additional options

Additionally to the parameters the package supports a list of options that can be passed to the functions. These include the model choice, the temperature and the amount of preprocessing. 

- **model**: Choose a LLM model. Supported models include ```'Llama-3.3-70B' (default)```, ```'mistral-small'```, ```'gemma-3-27b-it'```, ```'gemma-3'```, ```'gpt-oss-120b'```, ```'Apertus-8B-Instruct-2509'```. 
- **temperature**: Overrides the server default which is (NOT_GIVEN)

All these options can be called in the functions as follows:

```{r}
results_options <- llm_code(df, abstract, rules, 
                            options = list(model = 'mistral-small',
                                           temperature = "2")
                            )

results_options <- llm_code(results_options)

View(results_options)

```

## Custom Prompts for Coding

If you want to code and employing your own system prompt you can utilize the summary 
workflow which gives you more adaptability. Simply insert your system prompt as a text string like 
in the example below. Please note that you have to employ correct syntax (comma, quotation marks) for the code to work.

```{r}
custom_results <- llm_summarize(
  movies, abstract, rules, 
  options = list(
      prompts = list(
        system = c(
                  "You are an expert in content analysis. Be precise and concise.",
                  "Use the codebook provided to decide for each category, whether the text falls into the category.",
                  "Please carefully read the text and determine for each category whether it applies.",
                  "Return one line for each category. Each returned line must start with the category name", 
                  "followed by a colon ':' and then followed by one of the codes '5' if the category strongly applies,",
                  "'4' if it applies, '3' if you are unsure, '2' if it rather does not apply, and '1' if not at all.", 
                  "Return only the lines for each category - nothing else, no introduction, no explanation, no disclaimer!"),
        user = paste0(
          "# Rules:",
          "{{rules}}", 
          "# Text: ", 
          "`{{text}}`"
        )
    )
  )
)

custom_results <- llm_summarize(custom_results)

```

Using the summary workflow, the databoard server post-processes the result to split it into one field for each category.

## Custom prompts

If you want full customability we provide a custom prompt template. If you simply want to customize your system prompt for the multi coding process we advise you to adapt the llm_summarize() function as shown above, since this also handles pre- and post-processing of the data (e.g. making multiple columns in your dataframe for each category).

Within the llm_prompt function you can customize your prompt as follows:

```{r}

custom <- llm_prompt(
  movies, abstract,
  prompt.system = "Output a comma separated of coded categories. Just the list, nothing else. These are the possible categories': scifi, historical, drama, comedy, fantasy and romance",
  prompt.user = "{{text}}"
)

custom <- llm_prompt(custom)

print(custom$llm_result)
```



