---
title: "Getting started with the databoard"
output: html_document
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}
knitr::opts_chunk$set(eval=F, include=T)
```

## Introduction to the databoard package

**What is the idea behind the databoard package?**



**Main functionalities**

We are in an ongoing process to add more functionalities to the databoard. As of
now the service provides two main functionalities: to code text, to summarize text.

## Install the package and load the example data

First we load the package and get some data. Databoard can be installed from source using the remotes package. 
We are currently working to publish the package on cran.
To try out the package you can use one of the two internal dataframes *chat_gpt* or *movies*.

```{r data}
# Load the package
library(remotes)
remotes::install_github(datavana_databoard_r)

# Load an example data frame from the package
df_movies <- databoard::movies
df_chatgpt <- databoard::chatgpt

# Song examples
songs <- tribble(
  ~id, ~text,
  1,   "The Beatles, Hey Jude, 1968",
  2,   "Michael Jackson, Thriller, 1982",
  3,   "Queen, Bohemian Rhapsody, 1975",
  4,   "Adele, Rolling in the Deep, 2010",
  5,   "Bob Dylan, Like a Rolling Stone, 1965",
  6,   "Nirvana, Smells Like Teen Spirit, 1991",
  7,   "Madonna, Like a Virgin, 1984",
  8,   "Elton John, Your Song, 1970",
  9,   "Taylor Swift, Shake It Off, 2014",
  10,  "Billie Eilish, Bad Guy, 2019"
)

```

## Login into the service

To use the databoard service and the accompagnying package you need to have credentials. 
To obtain these please contact the [Digital Media and Computational Methods](https://www.uni-muenster.de/Kowi/en/institut/arbeitsbereiche/digital-media-computational-methods.shtml) 
research group. In the future we aim to open the service, but for now this is the only ways to use the package.

Once you have your credentials which consists of a username and a password 
you can log into the service. This login process stores your access token for 
the databoard API service invisibly in the system environment.

This storage and login lasts until you log out of the service. Please, especially 
when working on a shared computer, always remember to log out.  

```{r login}
# Login into the databoard service
da_login() #use the function as is. You will be asked to provide username and 
#password in a pop-up window.

# Logout of the databoard service
da_logout()

da_login()


```

## Using the service to code text

We use the ```llm_code()``` function to code text.
This function needs three arguments:

- the dataframe with the content you want to code
- the name of the column in which we can find the content (typically 'text')
- the codebook (see below) 

### Specify your codebook

The databoard accepts codebooks in form of a tibble data-object. If you have a csv file with the codebook information simply load it into R to use.

The codebook needs to be structures into three columns:

- category: the categories you want to code
- description: a short description of the category
- example: a short example

```{r codebook}
# Rule examples
rules <- tribble(
  ~category,    ~description, ~example,
  "pop",        "Popular music with catchy melodies and broad appeal", "Bruno Mars - Uptown Funk",
  "rock",       "Music characterized by strong beats and electric guitars", "Led Zeppelin - Stairway to Heaven",
  "hip hop",    "Rhythmic music often featuring rapping and DJing", "Eminem - Lose Yourself",
  "jazz",       "Music with swing and blue notes, improvisation, and complex harmonies", "John Coltrane - Giant Steps",
  "classical",  "Western art music from the medieval to the modern period", "Johann Sebastian Bach - Brandenburg Concerto No.3",
  "country",    "Music with roots in American folk and western styles", "Dolly Parton - Jolene",
  "electronic", "Music produced primarily with electronic instruments and synthesizers", "Calvin Harris - Summer",
  "rb",         "Rhythm and Blues featuring soulful vocals and groove-based instrumentation", "Mary J. Blige - Family Affair",
  "reggae",     "Music originating from Jamaica characterized by offbeat rhythms", "Peter Tosh - Legalize It",
  "metal",      "Loud, aggressive rock music with distorted guitars and emphatic rhythms", "Iron Maiden - The Trooper"
)

```

### Code data  with llms using two lines of code


```{r code}


# Submit without delay
data <- llm_code(songs, text, rules)

# Once you submitted your tasks, call the same method with
# your data frame as the first parameter
# Task results that are ready will be added.
# Keep calling until all result are finished.
data <- llm_code(data)

# Inspect result
count(data, llm_result)

```

### Additional parameters for coding

If you want to specify more parameters for coding you can use the more generic llm_summarize function which provides additional paramters. 

### Want individual prompts?

TEXT + eigene Vignette

## Using the service to summarize text

See also

```{rsummarize}

# Submit without delay
data <- llm_summarize(songs, text)

# Fetch and wait max 10 seconds for each case to finish
data <- llm_summarize(data)

# Inspect the summaries
head(data$llm_result)

```

## Trouble Shooting


```{r}
categories <- llm_summarize(
  songs, text, rules, mode="multi",
  options = list(
      prompts = list(
        system = paste0(
          "Carefully read the provided rules and the text.",
          "Determine for each category in the rules one keyword.",
          "Respond with one line per provided category.",
          "Start the line with the name of the category, followed by a colon and the suggested keyword.",
          "If you can't decide on a keyword, output `NA` for the respective category.",
          collapse="\n"
        ),
        user = paste0("# Rules:", "{{rules}}", "# Text: ", "`{{text}}`", collapse="\n")
    )
  ),
  wait=10
)
```

