---
title: "Getting started with the databoard"
output: html_document
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}

library(dplyr)
library(tibble)
knitr::opts_chunk$set(eval=FALSE, include=TRUE)
```

## Introduction to the databoard package

**What is the idea behind the databoard package?**



**Main functionalities**

We are in an ongoing process to add more functionalities to the databoard. As of
now the service provides two main functionalities: to code text, to summarize text.

## Install the package and load the example data

First we load the package and get some data. Databoard can be installed from source using the remotes package. 
We are currently working to publish the package on cran.

To try out the package you can use the internal dataframes *movies*, which contains 4 columns:
- an id
- the name of a movie
- a short abstract which can be used to code the data
- a long review, which can be employed to summarize the data

```{r data}
# Load the package

library(remotes)
remotes::install_github("datavana/databoard_r")

# Load an example data frame from the package

df <- databoard::movies # example data 

```

## Login into the service

To use the databoard service and the accompagnying package you need to have credentials. 
To obtain these please contact the [Digital Media and Computational Methods](https://www.uni-muenster.de/Kowi/en/institut/arbeitsbereiche/digital-media-computational-methods.shtml) 
research group. In the future we aim to open the service, but for now this is the only ways to use the package.

Once you have your credentials which consists of a username and a password 
you can log into the service. This login process stores your access token for 
the databoard API service invisibly in the system environment.
When you are succesfully logged in the message Logged in, access token saved in system environment" appears in the console.

This storage and login lasts until you close R or log out of the service. Please, especially 
when working on a shared computer, always remember to close the application or log out.  

```{r login}

# Login into the databoard service.
# You will be asked to provide username and password.
da_login() 

# Logout of the databoard service
da_logout()

```

## Using the service to summarize text

In our example dataframe ```movies``` we have a column ```review``` which features lengthy reviews of the moview plots. To summarize them into shorter paragraphs we use the llm_summarize function which only needs the dataframe and the column with the text to be summarized.


```{rsummarize}

# Submit without delay
results <- llm_summarize(df, review)

# Fetch and wait max 10 seconds for each case to finish
results <- llm_summarize(results)

# Inspect the summaries
head(results$llm_result, n=3)

```

## Using the service to code text

We use the ```llm_code()``` function to code text.
This function needs three arguments:

- the dataframe with the content you want to code
- the name of the column in which we can find the content (typically 'text')
- the codebook (see below) 

Within the databoard we have implemented various [systemprompts](https://github.com/datavana/databoard_core/tree/main/src/databoard_core/resources/prompts). The default prompt for the coding process is the single option categorizing each text into one category. See the customprompts vignette for further examples.

### Specify your codebook

Besides from the system prompt the databoard needs your individual codebook for coding. The databoard accepts codebooks in form of a tibble data-object. If you have a csv file with the codebook information simply load it into R to use.

The codebook needs to be structures into three columns:

- category: the categories you want to code
- description: a short description of the category
- example: a short example

We have implemented a example codebook for the dataset movies called movie_rules.

```{r codebook}
# Rule examples
rules <- databoard::movies_rules

```

### Code data  with llms using two lines of code

```{r code}

# Submit without delay
results <- llm_code(df, abstract, rules)

# Once you submitted your tasks, call the same method with
# your data frame as the first parameter
# Task results that are ready will be added.
# Keep calling until all result are finished.
results <- llm_code(results)

# Inspect result
library(dplyr)
count(results, llm_result)

```

## Whats Next

You can customize your prompts and vary different additional parameters. 
See the customprompts vignette for examples and further explanation. 

