---
title: "Getting Started"
output: html_document
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
devtools::load_all(".")

test <- iris |> slice_sample(n=15)

rules <- list(
    contain_v = list(
        category    = "contain_v",
        description = "Code when the word starts with a v",
        example     = "versicolor"
    ),
    contain_s = list(
        category    = "contain_s",
        description = "Code when setosa is mentioned",
        example     = "setosa"
    )
)

#db_login("", "")
db_test <- .submit_task(test, Species, task = "coding", rules = rules)
db_test <- .get_taskresult(db_test)

test3 <- llm_code(test, "Species", rules  = rules)
test4 <- llm_summarize(test, "Species")

```

## How to use the databoard package?

First we load the package and get some data. Databoard can be installed from source using the remotes package. 
We are currently working to publish the package on cran.
To try out the package you can use one of the two internal dataframes *chat_gpt* or *movies*.

```{r}
# Load the package
library(remotes)
remotes::install_github(datavana_databoard_r)

# Load an example data frame from the package
df_movies <- databoard::movies
df_chatgpt <- databoard::chatgpt

```

## Login into the service

To use the databoard service and the accompagnying package you need to have credentials. 
To obtain these please contact the [Digital Media and Computational Methods](https://www.uni-muenster.de/Kowi/en/institut/arbeitsbereiche/digital-media-computational-methods.shtml) 
research group. In the future we aim to open the service, but for now this is the only ways to use the package.

Once you have your credentials which consists of a username and a password 
you can log into the service. The login last for one session, 
after closing RStudio you have to renew the login process. 

```{r}
# Login into the service
db_login("username", "password") # please note, both username and password must be enclosed in quotation marks. 

```

This login process stores your access token for the databoard API service invisibly in the system environment.

## Core principles

TO BE ADDED

## The different functionalities of the databoard

We are in an ongoing process to add more functionalities to the databoard. As of
now the service provides three main functionalities: to code text, to summarize text
and to annotate text.

### Using the service to code text

```{r}
llm_code()
```

### Using the service to summarize text

```{r}
llm_summarize()
```

### Using the service to annotate text

## Additional Parameters


## Trouble Shooting



