---
title: "Getting started with the databoard"
output: html_document
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
# Example data

# Song examples
songs <- tribble(
  ~id, ~text,
  1,   "The Beatles, Hey Jude, 1968",
  2,   "Michael Jackson, Thriller, 1982",
  3,   "Queen, Bohemian Rhapsody, 1975",
  4,   "Adele, Rolling in the Deep, 2010",
  5,   "Bob Dylan, Like a Rolling Stone, 1965",
  6,   "Nirvana, Smells Like Teen Spirit, 1991",
  7,   "Madonna, Like a Virgin, 1984",
  8,   "Elton John, Your Song, 1970",
  9,   "Taylor Swift, Shake It Off, 2014",
  10,  "Billie Eilish, Bad Guy, 2019"
)

# Rule examples

rules <- tribble(
  ~category,    ~description, ~example,
  "pop",        "Popular music with catchy melodies and broad appeal", "Bruno Mars - Uptown Funk",
  "rock",       "Music characterized by strong beats and electric guitars", "Led Zeppelin - Stairway to Heaven",
  "hip hop",    "Rhythmic music often featuring rapping and DJing", "Eminem - Lose Yourself",
  "jazz",       "Music with swing and blue notes, improvisation, and complex harmonies", "John Coltrane - Giant Steps",
  "classical",  "Western art music from the medieval to the modern period", "Johann Sebastian Bach - Brandenburg Concerto No.3",
  "country",    "Music with roots in American folk and western styles", "Dolly Parton - Jolene",
  "electronic", "Music produced primarily with electronic instruments and synthesizers", "Calvin Harris - Summer",
  "rb",         "Rhythm and Blues featuring soulful vocals and groove-based instrumentation", "Mary J. Blige - Family Affair",
  "reggae",     "Music originating from Jamaica characterized by offbeat rhythms", "Peter Tosh - Legalize It",
  "metal",      "Loud, aggressive rock music with distorted guitars and emphatic rhythms", "Iron Maiden - The Trooper"
)

```


# Code
```{r include=FALSE}

# Login
da_login()

# Submit without delay
data <- llm_code(songs, text, rules)

# Once you submitted your tasks, call the same method with
# your data frame as the first parameter
# Task results that are ready will be added.
# Keep calling until all result are finished.
data <- llm_code(data)

# Inspect result
count(data, llm_result)

```


# Summarize

```{r}

# Submit without delay
data <- llm_summarize(songs, text)

# Fetch and wait max 10 seconds for each case to finish
data <- llm_summarize(data)

# Inspect the summaries
head(data$llm_result)

```

## How to use the databoard package?

First we load the package and get some data. Databoard can be installed from source using the remotes package. 
We are currently working to publish the package on cran.
To try out the package you can use one of the two internal dataframes *chat_gpt* or *movies*.

```{r}
# Load the package
library(remotes)
remotes::install_github(datavana_databoard_r)

# Load an example data frame from the package
df_movies <- databoard::movies
df_chatgpt <- databoard::chatgpt

```

## Login into the service

To use the databoard service and the accompagnying package you need to have credentials. 
To obtain these please contact the [Digital Media and Computational Methods](https://www.uni-muenster.de/Kowi/en/institut/arbeitsbereiche/digital-media-computational-methods.shtml) 
research group. In the future we aim to open the service, but for now this is the only ways to use the package.

Once you have your credentials which consists of a username and a password 
you can log into the service. The login last for one session, 
after closing RStudio you have to renew the login process. 

```{r}
# Login into the service
db_login("username", "password") # please note, both username and password must be enclosed in quotation marks. 

```

This login process stores your access token for the databoard API service invisibly in the system environment.

## Core principles

TO BE ADDED

## The different functionalities of the databoard

We are in an ongoing process to add more functionalities to the databoard. As of
now the service provides three main functionalities: to code text, to summarize text
and to annotate text.

### Using the service to code text

```{r}
llm_code()
```

### Using the service to summarize text

```{r}
llm_summarize()
```

### Using the service to annotate text

## Additional Parameters


## Trouble Shooting



