---
title: "Getting started with the databoard"
output: html_document
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}

library(dplyr)
library(tibble)
library(tidyr)

knitr::opts_chunk$set(eval=FALSE, include=TRUE)
```

# Introduction to the databoard package

With the Datavana Databoard service you can easily feed content into an LLM for automated analyses.´
After you submitted tasks, the data is processed in the background. 
Therefore, working with the service, always implies a two-step procedure.
Firstly, submit tasks and let the service do its work. 
Secondly, retrieve results.

The R package wraps the main functions of the service:

- `llm_summarize()` is used to condense text into shorter paragraphs or even single words.
   If you provide categories, one summary or keyword is returned for each category.
- `llm_code()` assigns predefined categories to a text. 
   Provide a codebook with category names, descriptions, and optionally examples. 
   Depending on your settings, the workflow will return one or multiple matching categories. 
- `llm_annotate()` adds in-text annotations, for example, to extract person or place names.
   According to your rule set, the matching text segments are enclosed in XML tags.

The predefined methods are based on pre-composed prompt templates and include pre- and post-processing steps aligned to the workflow. You can customize the prompts and several other options exposed by the service.

To gain full flexibility, use custom prompts and by-pass the processing steps:

- `llm_prompt()` fetches LLM answers using your own prompt templates. 

## Install the package and get example data

The Databoard package can be installed from source using the remotes package. 

```{r}

library(remotes)
remotes::install_github("datavana/databoard_r")
library(databoard)
```


To try out the package you can use the example data frame `movies`,
which contains four columns:  

- id: an identifier of the movie
- name: the movie title
- abstract: a short abstract, for example, to try genre detection using the coding workflow
- review: a longer review, for example, to try the summary workflow

```{r}

# Load example data from the package
df <- databoard::movies

```

## Login into the service

To obtain credentials for using the Databoard service, contact the [Digital Media and Computational Methods](https://www.uni-muenster.de/Kowi/en/institut/arbeitsbereiche/digital-media-computational-methods.shtml) 
research group.

Once you have a username and a password you can log into the service to get an access token. 
The `da_login()` method stores your access token invisibly in the system environment.

The login lasts until you close R or log out of the service. 
Please, when working on a shared computer, always remember to close the application or log out.  

```{r}

# Log into the Databoard service.
da_login()

# Log out of the Databoard service
da_logout()

```

The `da_login()` method prompts you to provide username and password.
See the function help for alternative ways to provide your credentials.

## Using the service to summarize text

In our example dataframe `movies` we have a column `review` which features lengthy reviews of the movies' plots. To summarize them into shorter paragraphs, use `llm_summarize()` and pass the data frame and the name of the column containing the review text.

```{r}

# Submit the tasks to the Databoard queue
results <- llm_summarize(df, review)

# Once you submitted the tasks, call the same method with
# the resulting data frame as the first parameter.
# Task results that are ready will be added by each call.
# The  wait-parameter defines how many seconds to wait at maximum for each case to finish.
results <- llm_summarize(results, wait = 10)

```

Within RStudio, inspect the `results` object to see the answers.


## Using the service to categorize text

Use the `llm_code()` function to categorize text.
The function expects three parameters:

- the data frame with the content you want to analyze
- the name of the column containing the text to be anlyzed
- a codebook defining coding rules as a data frame

The codebook data frame needs to contain three columns:

- category: the categories you want to code
- description: a description for each category
- example: optionally, for each category, provide matching examples

You can, for example, define it directly in R using the `tribble()` function
or prepare and load it from a csv or excel file with common tidyverse functions.

We have implemented an example codebook that can be used for playing with the example
movies dataset:

```{r}

# Rule examples
rules <- tibble::tribble(
  ~category,  ~description,                                                               ~example,
  "History",  "Movies based on real events or people from the past.",                     "Schindler’s List, Braveheart",
  "Scifi",    "Stories about futuristic science, technology, space, or alien life.",      "Interstellar, Blade Runner",
  "Musical",  "Films where characters sing and dance as part of the story.",              "The Greatest Showman, Mamma Mia",
  "Fantasy",  "Movies featuring magical or supernatural elements and imaginary worlds.",  "Pan’s Labyrinth, Harry Potter",
  "Comedy",   "Films made to entertain and make the audience laugh.",                     "Mean Girls, The Hangover",
  "Drama",    "Serious stories focused on relationships, and character development.",     "Forrest Gump, A Beautiful Mind"
)

```

Once you have data and rules, let the LLM categorize your text:

```{r}

# Submit
results <- llm_code(df, abstract, rules)

# Keep calling until all tasks are finished.
results <- llm_code(results)

# Inspect result
count(results, llm_result)

```

What about movies that fall into multiple categories? Try it out! 
Set the mode-parameter to "multi" and obtain a value between 0 to 2 for each category:


```{r}

# Submit
results <- llm_code(df, abstract, rules, mode="multi")

# Keep calling until all tasks are finished.
results <- llm_code(results)

```


## Using the service to annotate text

Use `llm_annotate()` to extract and annotate text spans according to rules.
The rules object is mandatory in submit mode and must provide three columns:

- `category`: used as `value` attribute in the annotation
- `description`: used to identify text segments
- `example`: comma-separated example segments that match the rule

The result contains the matching text segment wrapped in XML-tags.

```{r}

anno_rules <- tibble::tribble(
  ~category, ~description, ~example,
  "PERSON", "Names of people", "John Doe, Jane Roe",
  "PLACE", "Names of places", "Berlin, New York"
)

# Submit
results <- llm_annotate(df, abstract, anno_rules)

# Fetch pending tasks
results <- llm_annotate(results)


```

In addition, you will find a `llm_annos` column containing a data frame 
with the extracted segments for each case. Unnest them to get a simple 
data frame:

```{r}

segments <- results |> 
  select(id, name, llm_annos) |> 
  tidyr::unnest(llm_annos)

```

## What's next?

Customize your prompts and learn about additional model parameters in the 
customprompts vignette.
